Joint Likelihood Deconvolution of Astronomical Images in the Presence of Poisson Noise

### 2024-02-15 src/tex/ms.tex
[showyourwork] overleaf sync

    \begin{equation}
        \label{eq:approx-sigma}
        \rho(N_{\mathrm{Data}}, N_{\mathrm{Pred}}) \approx \frac{\hat{N}_{\mathrm{Data}} - \hat{N}_{\mathrm{Pred}}} {\sqrt{\hat{N}_{\mathrm{Pred}}}}.
    \end{equation}
where $\hat{N}$ is the weighted sum of counts from a Gaussian smoothing kernel with $\sigma_{\mathrm{smooth}}=5$ pixels. \dvd{I don't understand this notation. Do you mean that you apply kernal density estimation to the data and their predicted values under the model, using a Gaussian kernel wtith $\simgam=5$?}  The result is shown in the right panel of Figure~\ref{fig:example-fermi-lat}. The image shows no systematic effects and a spatially homogeneous distribution of the residual noise. The resulting distribution of residual significances per pixel is centered at $\mu=-0.001$ with a width of $\sigma=0.991$, indicating a close agreement with a standard normal distribution, as expected for a good model of the emission. In Figure~\ref{fig:example-fermi-lat-non-calibrated} we also show the residuals per PSF class with and without the correction defined by Equation~\ref{eq:model-npred-calibration}. More details of the \fermi analysis are available at \url{https://github.com/jolideco/jolideco-fermi-examples}

>>>>

    \begin{equation}
        \label{eq:approx-sigma}
        \rho(N_{\mathrm{Data}}, N_{\mathrm{Pred}}) \approx \frac{\hat{N}_{\mathrm{Data}} - \hat{N}_{\mathrm{Pred}}} {\sqrt{\hat{N}_{\mathrm{Pred}}}}.
    \end{equation}
where $\hat{N}$ is the weighted sum of counts from a Gaussian smoothing kernel with $\sigma_{\mathrm{smooth}}=5$ pixels. \dvd{I don't understand this notation. Do you mean that you apply kernal density estimation to the data and their predicted values under the model, using a Gaussian kernel with $\sigma=5$?}  The result is shown in the right panel of Figure~\ref{fig:example-fermi-lat}. The image shows no systematic effects and a spatially homogeneous distribution of the residual noise. The resulting distribution of residual significances per pixel is centered at $\mu=-0.001$ with a width of $\sigma=0.991$, indicating a close agreement with a standard normal distribution, as expected for a good model of the emission. In Figure~\ref{fig:example-fermi-lat-non-calibrated} we also show the residuals per PSF class with and without the correction defined by Equation~\ref{eq:model-npred-calibration}. More details of the \fermi analysis are available at \url{https://github.com/jolideco/jolideco-fermi-examples}
